SimResults_Enet

### 2024-08-01 sim_1.bross/simResults_bross.Rmd
simulation results bross, lasso, enet

```{r load basic information, warning=FALSE, cache=TRUE}}
# global information
exposure <- "obese"
outcome <- "diabetes" 
investigator.specified.covariates <- 
  c(# Demographic
    "age.cat", "sex", "education", "race", 
    "marital", "income", "born", "year",

@@

```{r initialization before for-loop, warning=FALSE, cache=TRUE}}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

@@

```{r scenario: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}}
set.seed(42)

@@

```{r scenarioER: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}}
set.seed(42)

@@

```{r scenarioOR: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}}
set.seed(42)

>>>>

```{r load basic information, warning=FALSE, cache=TRUE}
# global information
exposure <- "obese"
outcome <- "diabetes" 
investigator.specified.covariates <- 
  c(# Demographic
    "age.cat", "sex", "education", "race", 
    "marital", "income", "born", "year",

@@

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

@@

```{r scenario: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}
set.seed(42)

@@

```{r scenarioER: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}
set.seed(42)

@@

```{r scenarioOR: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}
set.seed(42)

### 2024-08-01 sim_3.lasso/simResults_lasso.Rmd
simulation results bross, lasso, enet

```{r initialization before for-loop, warning=FALSE, cache=TRUE}}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

@@

```{r}
data <- tryCatch({
  readRDS(url(url))
}, error = function(e) {
  closeAllConnections()
  readRDS(url(url))
})
```

```{r scenario: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}}
set.seed(42)

@@

  proxy_lasso.i <- paste0("proxy_lasso.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```
```{r scenarioER: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}}
set.seed(42)

@@

  proxy_lasso.i <- paste0("proxy_lasso.ER.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.ER.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```
```{r scenarioOR: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}}
set.seed(42)

>>>>

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 5

@@

```{r scenario: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  proxy_lasso.i <- paste0("proxy_lasso.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```

```{r scenarioER: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  proxy_lasso.i <- paste0("proxy_lasso.ER.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.ER.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```

```{r scenarioOR: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}
set.seed(42)

### 2024-08-01 sim_4.enet/SimResults_Enet.Rmd
simulation results bross, lasso, enet

---
title: "SimResults_Lasso"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

@@

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 5

RD_lasso <- data.frame(RD = numeric(),
                       SE = numeric())
```

```{r scenario: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  lasso.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                 x = covar.mat, 
                                 type.measure='mse',
                                 family="binomial",
                                 alpha = 1, 
                                 nfolds = 5)
  coef.fit <- coef(lasso.fit,s='lambda.min',exact=TRUE)
  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
  proxy_lasso <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_lasso, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_lasso <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_lasso$ps
  data$w.l <- W.out_lasso$weights

  fit.OR_lasso <- glm(out.formula,
                      data = data,
                      weights = W.out_lasso$weights,
                      family= binomial(link = "logit"))
  fit.RD_lasso <- glm(out.formula,
                       data = data,
                       weights = W.out_lasso$weights,
                       family = gaussian(link= "identity"))
  sum.RD_lasso <- c(summary(fit.RD_lasso)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_lasso)[2,2]))

  RD_lasso[i,] <- sum.RD_lasso
  rownames(RD_lasso)[i] <- paste0("data.", i, "_lasso")

  proxy_lasso.i <- paste0("proxy_lasso.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```

```{r scenarioER: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  lasso.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                 x = covar.mat, 
                                 type.measure='mse',
                                 family="binomial",
                                 alpha = 1, 
                                 nfolds = 5)
  coef.fit <- coef(lasso.fit,s='lambda.min',exact=TRUE)
  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
  proxy_lasso <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_lasso, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_lasso <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_lasso$ps
  data$w.l <- W.out_lasso$weights

  fit.OR_lasso <- glm(out.formula,
                      data = data,
                      weights = W.out_lasso$weights,
                      family= binomial(link = "logit"))
  fit.RD_lasso <- glm(out.formula,
                       data = data,
                       weights = W.out_lasso$weights,
                       family = gaussian(link= "identity"))
  sum.RD_lasso <- c(summary(fit.RD_lasso)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_lasso)[2,2]))

  RD_lasso[i+a,] <- sum.RD_lasso
  rownames(RD_lasso)[i+a] <- paste0("ER.data.", i, "_lasso")

  proxy_lasso.i <- paste0("proxy_lasso.ER.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.ER.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```

```{r scenarioOR: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  lasso.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                 x = covar.mat, 
                                 type.measure='mse',
                                 family="binomial",
                                 alpha = 1, 
                                 nfolds = 5)
  coef.fit <- coef(lasso.fit,s='lambda.min',exact=TRUE)
  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
  proxy_lasso <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_lasso, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_lasso <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_lasso$ps
  data$w.l <- W.out_lasso$weights

  fit.OR_lasso <- glm(out.formula,
                      data = data,
                      weights = W.out_lasso$weights,
                      family= binomial(link = "logit"))
  fit.RD_lasso <- glm(out.formula,
                       data = data,
                       weights = W.out_lasso$weights,
                       family = gaussian(link= "identity"))
  sum.RD_lasso <- c(summary(fit.RD_lasso)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_lasso)[2,2]))

  RD_lasso[i+2*a,] <- sum.RD_lasso
  rownames(RD_lasso)[i+2*a] <- paste0("OR.data.", i, "_lasso")

  proxy_lasso.i <- paste0("proxy_lasso.OR.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.OR.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```

```{r read RD & SE results by lasso, warning=FALSE, cache=TRUE}
RD_lasso
```

```{r check intermediate results for each data by lasso, warning=FALSE, cache=TRUE}
# check RD & SE by lasso for each data, print:
#   sum.RD_lasso.n, sum.RD_lasso.ER.n, or sum.RD_lasso.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_lasso.1
sum.RD_lasso.ER.2

# check proxy selected by lasso for each data, print:
#   proxy_lasso.n, proxy_lasso.ER.n, or proxy_lasso.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_lasso.1
proxy_lasso.ER.3
```

>>>>

---
title: "SimResults_Enet"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

@@

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

RD_enet <- data.frame(RD = numeric(),
                       SE = numeric())
```

```{r scenario: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  enet.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                 x = covar.mat, 
                                 type.measure='mse',
                                 family="binomial",
                                 alpha = 0.5, 
                                 nfolds = 5)
  coef.fit <- coef(enet.fit,s='lambda.min',exact=TRUE)
  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
  proxy_enet <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_enet, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_enet <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_enet$ps
  data$w.l <- W.out_enet$weights

  fit.OR_enet <- glm(out.formula,
                      data = data,
                      weights = W.out_enet$weights,
                      family= binomial(link = "logit"))
  fit.RD_enet <- glm(out.formula,
                       data = data,
                       weights = W.out_enet$weights,
                       family = gaussian(link= "identity"))
  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))

  RD_enet[i,] <- sum.RD_enet
  rownames(RD_enet)[i] <- paste0("data.", i, "_enet")

  proxy_enet.i <- paste0("proxy_enet.", i)
  assign(proxy_enet.i, proxy_enet)
  sum.RD_enet.i <- paste0("sum.RD_enet.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```
```{r scenarioER: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  enet.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                 x = covar.mat, 
                                 type.measure='mse',
                                 family="binomial",
                                 alpha = 1, 
                                 nfolds = 5)
  coef.fit <- coef(enet.fit,s='lambda.min',exact=TRUE)
  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
  proxy_enet <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_enet, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_enet <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_enet$ps
  data$w.l <- W.out_enet$weights

  fit.OR_enet <- glm(out.formula,
                      data = data,
                      weights = W.out_enet$weights,
                      family= binomial(link = "logit"))
  fit.RD_enet <- glm(out.formula,
                       data = data,
                       weights = W.out_enet$weights,
                       family = gaussian(link= "identity"))
  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))

  RD_enet[i+a,] <- sum.RD_enet
  rownames(RD_enet)[i+a] <- paste0("ER.data.", i, "_enet")

  proxy_enet.i <- paste0("proxy_enet.ER.", i)
  assign(proxy_enet.i, proxy_enet)
  sum.RD_enet.i <- paste0("sum.RD_enet.ER.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```

```{r scenarioOR: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  enet.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                 x = covar.mat, 
                                 type.measure='mse',
                                 family="binomial",
                                 alpha = 1, 
                                 nfolds = 5)
  coef.fit <- coef(enet.fit,s='lambda.min',exact=TRUE)
  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
  proxy_enet <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_enet, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_enet <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_enet$ps
  data$w.l <- W.out_enet$weights

  fit.OR_enet <- glm(out.formula,
                      data = data,
                      weights = W.out_enet$weights,
                      family= binomial(link = "logit"))
  fit.RD_enet <- glm(out.formula,
                       data = data,
                       weights = W.out_enet$weights,
                       family = gaussian(link= "identity"))
  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))

  RD_enet[i+2*a,] <- sum.RD_enet
  rownames(RD_enet)[i+2*a] <- paste0("OR.data.", i, "_enet")

  proxy_enet.i <- paste0("proxy_enet.OR.", i)
  assign(proxy_enet.i, proxy_enet)
  sum.RD_enet.i <- paste0("sum.RD_enet.OR.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```

```{r read RD & SE results by enet, warning=FALSE, cache=TRUE}
RD_enet
```

```{r check intermediate results for each data by enet, warning=FALSE, cache=TRUE}
# check RD & SE by enet for each data, print:
#   sum.RD_enet.n, sum.RD_enet.ER.n, or sum.RD_enet.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_enet.1
sum.RD_enet.ER.2

# check proxy selected by enet for each data, print:
#   proxy_enet.n, proxy_enet.ER.n, or proxy_enet.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_enet.1
proxy_enet.ER.3
```
